Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-21 paper/main.tex
added figure reporting which devices participants used

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.6\textwidth]{figs/devices}
\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
  participants whose fitness tracking data came from each model of
  Fitbit device.  ``MobileTrack'' refers to participants who used
  smartphone accelerometer information to track their activity via the
  Fitbit smartphone app.
  ``Unknown''  denotes participants whose device information was not
  available from their available Fitbit data.}
\label{fig:devices}
\end{figure}
